\documentclass[a4paper,10pt]{article}

\usepackage[T1]{fontenc}
\usepackage[scaled=0.96]{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage[margin=1.15cm]{geometry}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[most]{tcolorbox}

\definecolor{resumeInk}{HTML}{323B4C}
\definecolor{resumeMuted}{HTML}{6D7480}
\definecolor{resumePaper}{HTML}{F7F7F5}
\definecolor{resumeRule}{HTML}{D8DDE3}
\definecolor{resumePale}{HTML}{E9EDF1}

\pagecolor{resumePaper}
\color{resumeInk}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{0pt}
\setlist[itemize]{leftmargin=1.2em, itemsep=1.5pt, topsep=2pt, parsep=0pt, partopsep=0pt}
\renewcommand{\labelitemi}{\textcolor{resumeInk}{\scriptsize$\bullet$}}

\newcommand{\sectionbar}[1]{%
  \vspace{7pt}
  \begin{tcolorbox}[
    enhanced,
    colback=resumeInk,
    colframe=resumeInk,
    boxrule=0pt,
    arc=0pt,
    left=7pt,
    right=7pt,
    top=4pt,
    bottom=4pt,
    width=\linewidth,
  ]
    {\color{white}\bfseries\fontsize{9.5}{11}\selectfont #1}
  \end{tcolorbox}
  \vspace{3pt}
}

\newcommand{\project}[4]{%
  \noindent\colorbox{resumeInk}{\rule{0pt}{13pt}\hspace{5pt}}\hspace{7pt}\textbf{\href{#2}{#1 | GitHub}}\hfill{\footnotesize\color{resumeMuted}#3}\\
  \hspace*{17pt}{\footnotesize\color{resumeMuted}#4}
  \vspace{1pt}
}

\newcommand{\role}[3]{%
  \noindent\colorbox{resumeInk}{\rule{0pt}{13pt}\hspace{5pt}}\hspace{7pt}\textbf{#1}\hfill{\footnotesize\color{resumeMuted}#2}\\
  \hspace*{17pt}{\footnotesize\color{resumeMuted}#3}
}

\newcommand{\skillrow}[2]{%
  \textbf{#1}\par
  {\footnotesize #2}\par\vspace{5pt}
}

\begin{document}

\begin{tabularx}{\linewidth}{X r}
  {\fontsize{24}{26}\selectfont\bfseries PARTH THAKRE} &
  \begin{tabular}{r}
    {\footnotesize +91-7420903522}\\
    {\footnotesize \href{mailto:parth@masycoda.com}{parth@masycoda.com}}\\
    {\footnotesize \href{https://github.com/parth-thakre}{github.com/parth-thakre}}\\
    {\footnotesize \href{https://www.linkedin.com/parthsthakre/}{linkedin.com/in/parthsthakre}}
  \end{tabular}
\end{tabularx}

\vspace{2pt}
{\Large AI Engineer \& Software Developer}\\[-2pt]
\textcolor{resumeRule}{\rule{\linewidth}{1.2pt}}
\vspace{2pt}

\sectionbar{PROFESSIONAL SUMMARY}
{\small\raggedright
B.Tech Computer Science graduate with honors in Artificial Intelligence and Data Science, currently working as an AI/ML Engineer Intern at MaSyCoDa Solutions. Builds practical AI/LLM systems: Azure AI Foundry apps, local-first desktop AI workspaces, retrieval/OCR pipelines, tool-calling agents, multi-model evaluation flows, and private infrastructure. Engineering bias: keep data boundaries explicit, own the runtime when it matters, and measure AI behavior through real artifacts instead of demo claims.
\par}

\vspace{3pt}
\begin{minipage}[t]{0.48\linewidth}
  \raggedright
  \sectionbar{TECHNICAL SKILLSETS}
  \skillrow{Languages}{Python, TypeScript, JavaScript, C/C++, Java, Bash}
  \skillrow{AI/LLM Systems}{Azure AI Foundry, Azure OpenAI, RAG, OCR, tool/function calling, MCP, prompt/schema design}
  \skillrow{Evaluation}{LLM benchmarks, multi-model orchestration, structured rubrics, simulation metrics, artifact schemas}
  \skillrow{Backend/Product}{FastAPI, Flask, Express, Node.js, REST APIs, SQLite, Pydantic, Zod}
  \skillrow{Frontend/Desktop}{React, Next.js, Vite, Electron, HTML, CSS}
  \skillrow{Infra \& Cloud}{Docker, Docker Compose, Linux, reverse proxies, Microsoft Azure, Azure AI Search, Microsoft Fabric}
  \skillrow{AI Coding Tools}{Codex, OpenCode, OpenClaw, agentic coding workflows}
  \skillrow{Microsoft Platforms}{Copilot Studio, Power Apps}

  \sectionbar{DELIVERY CREDIBILITY}
  \begin{itemize}
    \item Converts AI prototypes into shipped artifacts: Electron apps, FastAPI services, Dockerized agents, CLI packages, and rendered reports.
    \item Designs outputs clients can verify through citations, structured JSON contracts, debug traces, scorecards, and repeatable run artifacts.
    \item Works across Azure-hosted, local-first, and private infrastructure runtimes to balance integration speed with data-boundary control.
    \item Builds systems where models can search, call tools, use files, expose evidence, and recover from invalid or incomplete outputs.
  \end{itemize}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\linewidth}
  \raggedright
  \sectionbar{CLIENT DELIVERY SIGNALS}
  \begin{itemize}
    \item Reduced manual supply-chain query paths by wrapping Kinaxis worksheet access behind conversational, evidence-backed workflows.
    \item Built measurable evaluation loops: 4-phase blind tournaments, 5-axis AISB scorecards, per-call logs, and structured artifacts.
    \item Owns deployment and reliability practice through 20+ container private infrastructure operations, routing, monitoring, and recovery.
    \item Uses Codex, OpenCode, and OpenClaw to accelerate implementation, review, debugging, and iteration without skipping source-control discipline.
  \end{itemize}
\end{minipage}

\newpage

\begin{tabularx}{\linewidth}{X r}
  {\fontsize{20}{22}\selectfont\bfseries PARTH THAKRE} &
  \begin{tabular}{r}
    {\footnotesize \href{mailto:parth@masycoda.com}{parth@masycoda.com}}\\
    {\footnotesize \href{https://github.com/parth-thakre}{github.com/parth-thakre}}
  \end{tabular}
\end{tabularx}
\textcolor{resumeRule}{\rule{\linewidth}{1.2pt}}

\begin{minipage}[t]{0.66\linewidth}
  \raggedright
  \sectionbar{SELECTED AI/LLM PROJECTS}

  \project{Threads}{https://github.com/parth-thakre/threads}{Electron, React, TypeScript, Azure AI Foundry}{Local-first desktop AI workspace}
  \begin{itemize}
    \item Built an Azure-backed desktop chat app with Entra/API-key auth, 200-chat local persistence caps, search, memory, and retrieval.
    \item Implemented extraction/OCR for 8+ file families: PDFs, DOCX, PPTX, XLSX, CSV, Markdown, text/code files, and scanned images.
    \item Added MCP tool discovery/selection, Azure web-search grounding, Claude Foundry routing, and GPT-image generation/editing flows.
  \end{itemize}

  \project{Story Tourney}{https://github.com/parth-thakre/story-tourney}{Node.js, TypeScript, Next.js, SQLite}{Blind multi-model LLM evaluation platform}
  \begin{itemize}
    \item Orchestrated 2-4 OpenRouter models through 4 structured phases: generation, blind peer review, revision, and final ranking.
    \item Added 4 Zod-validated JSON contracts, provider-call archives, encrypted OpenRouter key storage, and deterministic mock fallback.
    \item Implemented Borda-count scoring with first-place and peer-review tie-breakers for repeatable tournament outcomes.
  \end{itemize}

  \project{SemKerBot}{https://github.com/parth-thakre/SemKerBot-updated-teams}{Python, FastAPI, Semantic Kernel, Docker}{Kinaxis supply-chain query agent}
  \begin{itemize}
    \item Built a local-only agent/API split where Semantic Kernel tools query a FastAPI wrapper around Kinaxis RapidResponse worksheet data.
    \item Added 8 diagnostic playbooks, catalog-aware query planning, column-ID filter guidance, and per-call debug metrics.
    \item Enforced evidence-backed answers with workbook, worksheet, column, row, filter, and exact-value citations.
    \item Supported Azure OpenAI and local OpenAI-compatible runtimes such as LM Studio/Ollama through configurable deployment settings.
  \end{itemize}

  \project{AISB}{https://github.com/parth-thakre/project3}{Python, CLI, Simulation, Benchmarking}{AI Society Benchmark}
  \begin{itemize}
    \item Created an LLM benchmark that runs 5-role artificial societies with resources, trust, influence, resentment, and role-specific actions.
    \item Refactored toward an 18-module package CLI, canonical data layout, typed artifact schemas, and structured event logs.
    \item Replaced single-metric judging with 5-axis scorecards for welfare, economy, cohesion, institutions, and anti-degeneracy.
  \end{itemize}

  \sectionbar{WORK EXPERIENCE}
  \role{MaSyCoDa Solutions Pvt. Ltd.}{Dec 2025 - Present}{AI/ML Engineer Intern | Pune}
  \begin{itemize}
    \item Built enterprise AI prototypes across 5 Microsoft/Azure surfaces: Azure Portal, AI Foundry, Azure OpenAI, AI Search, and Fabric.
    \item Connected Azure AI Foundry agents with Copilot Studio and Power Apps integration surfaces for client-facing automation demos.
    \item Deployed an internal Kinaxis RapidResponse supply-chain agent that reduced manual worksheet lookup through evidence-backed Q\&A.
    \item Added 8 diagnostic playbooks, citation requirements, and per-call debug traces to make supply-chain answers repeatable and auditable.
    \item Used Codex, OpenCode, OpenClaw, and agentic coding harnesses to accelerate implementation, review, debugging, and iteration.
  \end{itemize}
\end{minipage}
\hfill
\begin{minipage}[t]{0.30\linewidth}
  \raggedright
  \sectionbar{EDUCATION}
  \textbf{Shri Ramdeobaba College of Engineering and Management}\\
  {\footnotesize B.Tech in Computer Science and Engineering}\\
  {\footnotesize Honors in AI and Data Science}\\
  {\footnotesize Final CGPA: 7.7 \hfill 2022 - June 2026}

  \vspace{6pt}
  \textbf{Taywade College}\\
  {\footnotesize Higher Secondary Certificate \hfill 2022}

  \vspace{6pt}
  \textbf{Bhavan's Trimurti Nagar School}\\
  {\footnotesize CBSE \hfill 2020}

  \sectionbar{PRIVATE INFRASTRUCTURE}
  {\footnotesize
  Operates a private 20+ container Linux infrastructure lab covering self-hosted services, AI tooling, reverse proxy routing, monitoring, and recovery. Uses it to practice deployment discipline, privacy-aware runtime design, and service reliability.
  }
\end{minipage}

\end{document}
